\LARGE \bf Child-Robot Spatial Arrangement in a Learning by Teaching Activity

### 2016-05-25 paper-Ro_Man-2016.tex
fix figue evol feedback
some typos

\author{Wafa Johal$^{1}$$^{2}$, Alexis Jacq$^{1}$$^{3}$, Ana Paiva$^{3}$ and Pierre Dillenbourg$^{1}$  % <-this % stops a space
\thanks{}% <-this % stops a space
\thanks{$^{1}$ CHILI Lab,
	$^{2}$ LSRO Lab,
        \'{E}cole F\'{e}d\'{e}rale Polytechnique Lausanne, Switzerland
        {\tt\small firstname.lastname@epfl.ch}}%
\thanks{$^{3}$Instituto Superior T\'{e}cnico, University of Lisbon, Portugal
        {\tt\small firstname.lastname@inesc-id.pt}}%
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper, we present an experiment in the context of a child-robot interaction where we study the influence of the child-robot spatial arrangement on the child's focus of attention and the perception of the robot's performance. In the ``Co-Writer learning by teaching'' activity, the child teaches a Nao robot how to handwrite.
Usually only face-to-face spatial arrangements are tested in educational child robot interactions, but we explored two spatial conditions from Kendon's F-formation, the side-by-side and the face-to-face formations in a within subject experiment.
We estimated the gaze behaviour of the child and their consistency in grading the robot with regard to the robot's progress in writing. 
Even-though the demonstrations provided by children were not different between the two conditions (i.e. the robot's learning didn't differ),  the results showed that in the side-by-side condition children tended to be more indulgent with the robot's mistakes and to give it better feedback.
These results highlight the influence of experimental choices in child-robot interaction.
%These results will allow us to take into account the variability of the judgement of the children relatively to the robot's performances.
\end{abstract}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{figures/plots/evoldemocondbis}
	\caption{Evolution of Feedback along the demonstration index(Mean: line , SD: filled area)}
	\label{fig:uf_nb}
\end{figure}
Even though the average feedback was increasing along with the number of demonstration for both condition, they don't seems to increase the same way(see Figure\ref{fig:uf_nb})
The effect of the F-Formation on the feedback from the child was statistically significant (Anova Repeated measures within subjects: $F_{1,272}= 4.396, p<0.05$). As, illustrated on Figure \ref{fig:userfeedback_fformation_se}, the average feedback per demonstration was greater($M=0.03, SD=1, N=147$) for the side-by-side condition compare to the face-to-face condition ($M=-0.23, SD=0.98, N=138$).
 \begin{figure}
 	\centering
 	\includegraphics[width=0.58\linewidth]{figures/plots/userfeedback_fformation_se}
 	\caption{Feedback Sum According to the F-Formation (Means and Confidence Intervals)}
 	\label{fig:userfeedback_fformation_se}
 \end{figure}

>>>>

\author{Wafa Johal$^{1}$$^{2}$, Alexis Jacq$^{1}$$^{3}$, Ana Paiva$^{3}$ and Pierre Dillenbourg$^{1}$  % <-this % stops a space
\thanks{}% <-this % stops a space
\thanks{$^{1}$ CHILI Lab,
	$^{2}$ LSRO Lab,
        \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Switzerland
        {\tt\small firstname.lastname@epfl.ch}}%
\thanks{$^{3}$Instituto Superior T\'{e}cnico (IST), University of Lisbon, Portugal
        {\tt\small firstname.lastname@inesc-id.pt}}%
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper, we present an experiment in the context of a child-robot interaction where we study the influence of the child-robot spatial arrangement on the child's focus of attention and the perception of the robot's performance. In the ``Co-Writer learning by teaching'' activity, the child teaches a Nao robot how to handwrite.
Usually only face-to-face spatial arrangements are tested in educational child robot interactions, but we explored two spatial conditions from Kendon's F-formation, the side-by-side and the face-to-face formations in a within subject experiment.
We estimated the gaze behavior of the child and their consistency in grading the robot with regard to the robot's progress in writing. 
Even-though the demonstrations provided by children were not different between the two conditions (i.e. the robot's learning didn't differ),  the results showed that in the side-by-side condition children tended to be more indulgent with the robot's mistakes and to give it better feedback.
These results highlight the influence of experimental choices in child-robot interaction.
%These results will allow us to take into account the variability of the judgement of the children relatively to the robot's performances.
\end{abstract}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{figures/plots/evoldemocondbis}
	\caption{Evolution of Feedback along the demonstration index(Mean: line , Confidence Interval 0.95: filled area)}
	\label{fig:uf_nb}
\end{figure}
Even though the average feedback was increasing along with the number of demonstration for both condition, they don't seems to increase the same way(see Figure\ref{fig:uf_nb})
The effect of the F-Formation on the feedback from the child was statistically significant (Anova Repeated measures within subjects: $F_{1,272}= 4.396, p<0.05$). As, illustrated on Figure \ref{fig:userfeedback_fformation_se}, the average feedback per demonstration was greater($M=0.03, SD=1, N=147$) for the side-by-side condition compare to the face-to-face condition ($M=-0.23, SD=0.98, N=138$).
 \begin{figure}
 	\centering
 	\includegraphics[width=0.58\linewidth]{figures/plots/userfeedback_fformation_se}
 	\caption{Feedback Sum According to the F-Formation (Means and Confidence Intervals)}
 	\label{fig:userfeedback_fformation_se}
 \end{figure}
